Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-03-03 xrb/submit/paper.tex

We also considered the effect of the network size.
Figure~\ref{fig:network} shows a comparison of the 10/10 boosting run
with the standard 13-isotope {\tt aprox13} network and the reduced
7-isotope {\tt iso7} network.  We see that the flame in the {\tt aprox13}
case is slightly more advanced and has a higher $\bar{A}$ than the {\tt iso7}
case.  We see in the next section that these two networks give largely
the same flame speed.  We only ran the simulation with the {\tt iso7}
reaction network to 15~ms, and we observe this was sufficient to establish
a steady flame speed for comparison to our 10/10 simulation with the {\tt aprox13}
network. The reduced network size saves a lot of memory, which will be useful when we
transition to 3D simulations.

@@

Table \ref{table:flame_speeds_multid} gives the flame speed measured in each multidimensional
simulation. The 2D flames propagate at speeds about an order of magnitude faster than their 1D
counterparts (Table \ref{table:flame_speeds_1d}). The increase in flame speed is likely a product
of the larger flame surface area and hydrodynamical effects such as turbulence, wrinkling, and
convective cycles, which bring cooler fuel from ahead of the front into the hottest part of the
burning region.

>>>>

We also considered the effect of the network size.
Figure~\ref{fig:network} shows a comparison of the 10/10 boosting run
with the standard 13-isotope {\tt aprox13} network and the reduced
7-isotope {\tt iso7} network.  We see that the flame in the {\tt aprox13}
case is slightly more advanced and has a higher $\bar{A}$ than the {\tt iso7}
case.  We see in the next section that these two networks give largely
the same flame speed. \added{We only ran the simulation with the {\tt iso7}
reaction network out to 15~ms, and we observe this was sufficient to establish
a steady flame speed for comparison to our 10/10 simulation with the {\tt aprox13}
network.} The reduced network size saves a lot of memory, which will be useful when we
transition to 3D simulations.

@@

Table \ref{table:flame_speeds_multid} gives the flame speed measured in each multidimensional
simulation. \added{Uncertainties in the velocities are the standard errors of the slopes returned by the
least-squares fits, assuming uncertainties in front position on the order of the coarse grid size.}
The 2D flames propagate at speeds about an order of magnitude faster than their 1D counterparts
(Table \ref{table:flame_speeds_1d}). The increase in flame speed is likely a product of the larger
flame surface area and hydrodynamical effects such as turbulence, wrinkling, and convective cycles,
which bring cooler fuel from ahead of the front into the hottest part of the burning region.
